---
title: "Untitled"
author: "Felicia Zhang"
date: '2018-01-24'
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2) 
library(zoo)
library(reshape)
library(plyr)
library(dplyr)
library(scales) 
library(data.table)
library(signal)
library(matrixStats)
library(lme4)
library(arm)
library(RColorBrewer)
library(lmerTest)
library(boot)

# load preprocessed data
orig.sample.a <- read.csv("/Volumes/emberson/ResearchProjects/Pupillometry/Pinwheels14/Pinwheel14_1-10_Infant_Preprocessed_RemovedOutliers.csv")
orig.sample.a$X <- NULL
orig.sample.b <- read.csv("/Volumes/emberson/ResearchProjects/Pupillometry/Pinwheels14/Pinwheel14_11-17_Infant_Preprocessed_RemovedOutliers.csv")
orig.sample.b$X <- NULL

#combine
orig.sample <- rbind(orig.sample.a,orig.sample.b)

# excluded trial 1 of each preswitch sub-block
orig.sample2 <- subset(orig.sample, !(switch==1 & trialnum==1))

# orig.sample = trials with more than 50% looking
# orig.sample2 = excluded trial 1 of each preswitch sub-block
```

Percentage of experiment completed per subject
```{r}
v1 <- ddply(orig.sample2,.(subID),summarise,totaltrials=length(unique(TRIAL_INDEX,na.rm = TRUE)))  
v1$percent <- v1$totaltrials/51 #have to divide by 51, becaue original study is 48 trials, but then we split postswitch trial 1  into 2 so it's 48+3
z <- mean(v1$percent)

ggplot(v1,aes(x=factor(subID),y=percent))+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat="identity")+
  ggtitle("Percent of experiment completed after exclusion criteria")+
  labs(x = "Subject ID", y = "% of experiment completed (# of trials/51)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(labels = scales::percent,limits=c(0,1),breaks=seq(0,1,.1))+
  geom_hline(yintercept = z, color="coral",size=1.5)

```

REMOVE BAD SUBJECTS
```{r}
orig.sample2 <- subset(orig.sample2, subID != 1)
orig.sample2 <- subset(orig.sample2, subID != 2)
orig.sample2 <- subset(orig.sample2, subID != 4)
orig.sample2 <- subset(orig.sample2, subID != 6)
orig.sample2 <- subset(orig.sample2, subID != 8)
orig.sample2 <- subset(orig.sample2, subID != 11)
orig.sample2 <- subset(orig.sample2, subID != 15)
orig.sample2 <- subset(orig.sample2, subID != 17)
```

AEM coding
```{r}
poo <- orig.sample2

#1. Binning every 100ms, to make sure that it's actually a fixation for lookstotarget
moo <- data.frame(subID=numeric(),trialnum=numeric(),timecode=numeric(),block=numeric(),switch=numeric(),lookingattarget=numeric())
subs <- unique(poo$subID)
time <- seq(100,4000, by=100) #the time bins we are trying to create (0-4000ms) doing 4000ms 

for (j in 1:length(subs)) {
  #gets every trial for 1 subject
  trials <- unique(poo$TRIAL_INDEX[poo$subID==subs[j]])
  print(j)
  for (i in 1:length(trials)) {
    #gets all sample for 1 trial  
    woo <- subset(poo, subID==subs[j] & TRIAL_INDEX == trials[i])
    c <- woo$block[1]
    cc <- woo$switch[1]
    ccc <- woo$trialnum[1]
    for (k in 1:length(time)){
      #for every 25 sample/100 ms, get lookattarget column
      if (k==1) {
        target <- woo$lookattarget[woo$TIMECODE < time[k]+1] #gets 0-100ms
        d <- unique(target)
        dd <- which(d==1)
      } else {
        target <- woo$lookattarget[woo$TIMECODE < time[k]+1 & woo$TIMECODE > time[k-1]-1]
        d <- unique(target)
        dd <- which(d==1)
      }
      #see if entire chunk is looking at target
      if (length(target)==0) { #no samples collected during this time
        aa <- c(subs[j],trials[i],ccc,c,cc,time[k],99)   
        moo <- rbind(moo,aa)
        warnings()
      } else if (length(d)==1 & d==1) { #looking at target entire time
        aa <- c(subs[j],trials[i],ccc,c,cc,time[k],d)   
        moo <- rbind(moo,aa)
        warnings()
      } else if (length(d)==1 & d==0) { #looking at distractor entire time
        aa <- c(subs[j],trials[i],ccc,c,cc,time[k],d)   
        moo <- rbind(moo,aa)
        warnings()
      } else if (length(d)==1 & d==5) { #looking at center entire time
        aa <- c(subs[j],trials[i],ccc,c,cc,time[k],d)   
        moo <- rbind(moo,aa)
        warnings()
      } else if (length(d) > 1 & length(dd) < 1) { #not looking at same location and not looking at target (looking at distractor and center)
        aa <- c(subs[j],trials[i],ccc,c,cc,time[k],9)   
        moo <- rbind(moo,aa) 
        warnings()
      } else { #not looking at same location and but looking at target sometimes
        #calculate proportion looking  
        b <- length(which(target==1)) #samples where subs are looking at target
        bb <- length(which(target==1))/length(target) #looking at target/25
        aa <- c(subs[j],trials[i],ccc,c,cc,time[k],bb) 
        moo <- rbind(moo,aa)
        warnings()
      }}}}

names(moo)[1] <- "subID"
names(moo)[2] <- "trialnum"
names(moo)[3] <- "trialnum2"
names(moo)[4] <- "block"
names(moo)[5] <- "switch"
names(moo)[6] <- "timecode"
names(moo)[7] <- "lookattarget"

#0 = distractor, 1 = target, 5 = center, 9 = looking at distractor and center, 99 = no data collected
x1 <- subset(moo, lookattarget < 99) #remove no data collected
x1$looktocenter <- 0

#coding which trials looked to center before making AEM
subs <- unique(x1$subID)
for (j in 1:length(subs)) {
  #gets every trial for 1 subject
  trials <- unique(x1$trialnum[x1$subID==subs[j]])
  print(j)
  for (i in 1:length(trials)) {
    foo <- subset(x1, subID==subs[j] & trialnum==trials[i] & timecode < 701)  
    if (any(foo$lookattarget==5)) {
      x1$looktocenter[x1$subID==subs[j] & x1$trialnum==trials[i]] <- 1
    }
  }}

#code trial type: pupil match, pupil mismatch, or no AEM 
#must look to center first, must make eye movement in 700-2700ms
#type 1 = pupil match, 2 = pupil mismatch, 3 = no AEM

x1$type <- 3
subs <- unique(x1$subID)

for (j in 1:length(subs)) {
  #gets every trial for 1 subject
  trials <- unique(x1$trialnum[x1$subID==subs[j]])
  print(j)
  for (i in 1:length(trials)) {
    #current trial
    foo <- subset(x1, subID==subs[j] & trialnum==trials[i] & timecode > 699 & timecode <2601) 
    if (any(foo$lookattarget==0) & foo$looktocenter[1]==1) {
      x1$type[x1$subID==subs[j] & x1$trialnum==trials[i]] <- 2
    }
    if (any(foo$lookattarget==1) & foo$looktocenter[1]==1) {
      x1$type[x1$subID==subs[j] & x1$trialnum==trials[i]] <- 1
    }
    }
  }

pupilbreakdown <- x1
```

add in trialtype info into main DF
Recode every trial two times
-correct vs incorrect for AEM
-match vs mismatch for the pupil 
```{r}
# match vs mismatch for the pupil 
z1 <- ddply(pupilbreakdown,.(subID,trialnum,trialnum2),summarise,trialtype=(unique(type,na.rm = TRUE)))  
z1 <- subset(z1, trialtype < 3)

orig.sample2$trialtype.pupil <- 3

for (j in 1:length(z1$subID)) {
  x <- z1$subID[j]
  y <- z1$trialnum[j]
  y2 <- z1$trialnum2[j]
  z <- z1$trialtype[j]
  orig.sample2$trialtype.pupil[orig.sample2$subID==x & orig.sample2$TRIAL_INDEX==y & orig.sample2$trialnum==y2] <- z
}
# type 1 = pupil match, 2 = pupil mismatch, 3 = no AEM

# correct vs incorrect for AEM
orig.sample2$trialtype.aem <- orig.sample2$trialtype.pupil
#only trial 1 of post-switch switches labelling, unless it's 3
orig.sample2$trialtype.aem[orig.sample2$trialtype.pupil==1 & orig.sample2$trialnum==1 & orig.sample2$switch==2] <- 2
orig.sample2$trialtype.aem[orig.sample2$trialtype.pupil==2 & orig.sample2$trialnum==1 & orig.sample2$switch==2] <- 1
#type 1 = correct aem, 2 = incorrect aem, 3 = no AEM

#checking to make sure the correct trials were recoded
foo <- ddply(orig.sample2,.(subID,TRIAL_INDEX,trialtype.aem),summarise,trialtype.pupil=unique(trialtype.pupil,na.rm = TRUE))
foo$diff <- foo$trialtype.aem - foo$trialtype.pupil 
```

Recode post-switch trial 1
```{r}
orig.sample2a <- subset(orig.sample2, switch==1)
orig.sample2a <- subset(orig.sample2a, trialnum > 1)
orig.sample2a$NEWTRIALNUM <- orig.sample2a$trialnum
#2-9 for pre, 1-8 for post

orig.sample2b <- subset(orig.sample2, switch==2)
orig.sample2b$NEWTRIALNUM <- orig.sample2b$trialnum 

#relabel center and aem time period as preswitch trial 9
orig.sample2b$switch[orig.sample2b$TIMECODE < 2701 & orig.sample2b$trialnum==1] <- 1
orig.sample2b$NEWTRIALNUM[orig.sample2b$TIMECODE < 2701 & orig.sample2b$trialnum==1] <- 9

orig.sample5 <- rbind(orig.sample2a,orig.sample2b)

orig.sample5$TRIAL_INDEX[orig.sample5$switch==1 & orig.sample5$NEWTRIALNUM==9 & orig.sample5$block==1] <- 101
orig.sample5$TRIAL_INDEX[orig.sample5$switch==1 & orig.sample5$NEWTRIALNUM==9 & orig.sample5$block==2] <- 201
orig.sample5$TRIAL_INDEX[orig.sample5$switch==1 & orig.sample5$NEWTRIALNUM==9 & orig.sample5$block==3] <- 301
```

Percentage of experiment completed per subject
```{r}
v1 <- ddply(orig.sample5,.(subID),summarise,totaltrials=length(unique(TRIAL_INDEX,na.rm = TRUE)))  
v1$percent <- v1$totaltrials/51 #have to divide by 51, becaue original study is 48 trials, but then we split postswitch trial 1  into 2 so it's 48+3
z <- mean(v1$percent)

ggplot(v1,aes(x=factor(subID),y=percent))+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat="identity")+
  ggtitle("Percent of experiment completed after exclusion criteria")+
  labs(x = "Subject ID", y = "% of experiment completed (# of trials/51)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(labels = scales::percent,limits=c(0,1),breaks=seq(0,1,.1))+
  geom_hline(yintercept = z, color="coral",size=1.5)

```

Average percentage looking per subject
```{r}
hoo <- ddply(orig.sample5,.(subID, TRIAL_INDEX),summarise,trackloss=mean(trackloss,na.rm = TRUE))
hoo2 <- ddply(hoo,.(subID),summarise,tracklosssub=mean(trackloss,na.rm = TRUE),setrials=sd(trackloss, na.rm = TRUE)/sqrt(length(trackloss)))

hoo2$looking <- 1-hoo2$tracklosssub
z <- mean(hoo2$looking)

limits <- aes(ymax = looking + setrials, ymin=looking - setrials)

ggplot(hoo2,aes(x=factor(subID),y=looking))+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat="identity")+
  ggtitle("Percent looking average for each baby")+
  labs(x = "Subject ID", y = "% looking (averaged across all trials)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  theme(plot.title = element_text(hjust = 0.5))+
  scale_y_continuous(labels = scales::percent,limits=c(0,1),breaks=seq(0,1,.1))+
  geom_hline(yintercept = z, color="coral",size=1.5)+
  geom_errorbar(limits, width=0.25,color="black")
```

summary graph: aem correct/incorrect percentage for each subject
```{r}
#total number of trials completed by subject
v1 <- ddply(orig.sample5,.(subID,TRIAL_INDEX),summarise,aemtrialtype=unique(trialtype.aem,na.rm = TRUE))
v2 <- ddply(v1,.(subID),summarise,numoftrials=length(unique(TRIAL_INDEX,na.rm = TRUE)))

#grouping trials into trialtypes
v.cor <- subset(v1, aemtrialtype==1)
v.incor <- subset(v1, aemtrialtype==2)
v.no <- subset(v1, aemtrialtype==3)

#total number of trials for each trial type  
v.cor2 <- ddply(v.cor,.(subID),summarise,numoftrials=length(unique(TRIAL_INDEX,na.rm = TRUE)))
v.incor2 <- ddply(v.incor,.(subID),summarise,numoftrials=length(unique(TRIAL_INDEX,na.rm = TRUE)))
v.no2 <- ddply(v.no,.(subID),summarise,numoftrials=length(unique(TRIAL_INDEX,na.rm = TRUE)))

#create empty dataframe
subs <- unique(orig.sample5$subID)
z <- length(subs)*3
moo <- data.frame(subID=numeric(z),trialtype=numeric(z),percent=numeric(z))
moo$subID <- subs
moo$trialtype <- rep(1:3, each = length(subs))

#calculate percent
#trialtype 1 (correct)
subs <- unique(moo$subID)
for (j in 1:length(subs)) { 
z <- which(v.cor2$subID==subs[j])
zz <- which(v2$subID==subs[j]) 
if (length(z)==0) { #if doesn't match
  moo$percent[j] <- NA
} else {
  moo$percent[j] <- v.cor2$numoftrials[z] / v2$numoftrials[zz]
}
} 

#trialtype 2 (incorrect)
subs <- unique(moo$subID)
for (j in 1:length(subs)) { 
z <- which(v.incor2$subID==subs[j])
zz <- which(v2$subID==subs[j]) 
if (length(z)==0) { #if doesn't match
  moo$percent[j+length(subs)] <- NA
} else {
  moo$percent[j+length(subs)] <- v.incor2$numoftrials[z] / v2$numoftrials[zz]
}
} 

#trialtype 3 (no AEM)
subs <- unique(moo$subID)
for (j in 1:length(subs)) { 
z <- which(v.no2$subID==subs[j])
zz <- which(v2$subID==subs[j]) 
if (length(z)==0) { #if doesn't match
  moo$percent[j+length(subs)*2] <- NA
} else {
  moo$percent[j+length(subs)*2] <- v.no2$numoftrials[z] / v2$numoftrials[zz]
}} 

#plot
moo$trialtype[1:length(subs)] <- 3
moo$trialtype[(length(subs)*2+1):(length(subs)*3)] <- 1
moo[is.na(moo)] <- 0 #replace NA with 0, to get rid of warning message

ggplot(moo,aes(x=factor(subID),y=percent,color=factor(trialtype),fill=factor(trialtype)))+
  geom_bar(stat="identity")+
  theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  labs(x = "Subject", y = "% of trials")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  guides(color=FALSE)+
  scale_fill_brewer(palette="Set3",name="Trial breakdown",breaks=c("1","2","3"),labels=c("no AEM", "incorrect AEMs","correct AEMs"))+
  scale_color_brewer(palette="Set3")+
  theme(legend.position = "bottom")+
  scale_y_continuous(labels = scales::percent,limits=c(0,1),breaks=seq(0,1,.2))

avgAEM <- mean(moo$percent[moo$trialtype==3])
avgIncorrectAEM <- mean(moo$percent[moo$trialtype==2])
avgNoAEM <- mean(moo$percent[moo$trialtype==1])
```

summary graph: pupil match/mismatch percentage for each subject
```{r}
#total number of trials completed by subject
w1 <- ddply(orig.sample5,.(subID,TRIAL_INDEX),summarise,pupiltrialtype=unique(trialtype.pupil,na.rm = TRUE))
w2 <- ddply(w1,.(subID),summarise,numoftrials=length(unique(TRIAL_INDEX,na.rm = TRUE)))

#grouping trials into trialtypes
w.match <- subset(w1, pupiltrialtype==1)
w.mismatch <- subset(w1, pupiltrialtype==2)
w.no <- subset(w1, pupiltrialtype==3)

#total number of trials for each trial type  
w.match2 <- ddply(w.match,.(subID),summarise,numoftrials=length(unique(TRIAL_INDEX,na.rm = TRUE)))
w.mismatch2 <- ddply(w.mismatch,.(subID),summarise,numoftrials=length(unique(TRIAL_INDEX,na.rm = TRUE)))
w.no2 <- ddply(w.no,.(subID),summarise,numoftrials=length(unique(TRIAL_INDEX,na.rm = TRUE)))

#create empty dataframe
subs <- unique(orig.sample5$subID)
z <- length(subs)*3
goo <- data.frame(subID=numeric(z),trialtype=numeric(z),percent=numeric(z))
goo$subID <- subs
goo$trialtype <- rep(1:3, each = length(subs))

#calculate percent
#trialtype 1 (match)
subs <- unique(goo$subID)
for (j in 1:length(subs)) { 
z <- which(w.match2$subID==subs[j])
zz <- which(w2$subID==subs[j]) 
if (length(z)==0) { #if doesn't match
  goo$percent[j] <- NA
} else {
  goo$percent[j] <- w.match2$numoftrials[z] / w2$numoftrials[zz]
}
} 

#trialtype 2 (mismatch)
subs <- unique(goo$subID)
for (j in 1:length(subs)) { 
z <- which(w.mismatch2$subID==subs[j])
zz <- which(w2$subID==subs[j]) 
if (length(z)==0) { #if doesn't match
  goo$percent[j+length(subs)] <- NA
} else {
  goo$percent[j+length(subs)] <- w.mismatch2$numoftrials[z] / w2$numoftrials[zz]
}
} 

#trialtype 3 (no AEM)
subs <- unique(goo$subID)
for (j in 1:length(subs)) { 
z <- which(w.no2$subID==subs[j])
zz <- which(w2$subID==subs[j]) 
if (length(z)==0) { #if doesn't match
  goo$percent[j+length(subs)*2] <- NA
} else {
  goo$percent[j+length(subs)*2] <- w.no2$numoftrials[z] / w2$numoftrials[zz]
}} 

#plot
goo$trialtype[1:length(subs)] <- 3
goo$trialtype[(length(subs)*2+1):(length(subs)*3)] <- 1
goo[is.na(goo)] <- 0 #replace NA with 0, to get rid of warning message

ggplot(goo,aes(x=factor(subID),y=percent,color=factor(trialtype),fill=factor(trialtype)))+
  geom_bar(stat="identity")+
  labs(x = "Subject", y = "% of trials")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  guides(color=FALSE)+
  scale_color_manual(values = c("#f1af8f", "#2398a0","#acc2c7"))+
  scale_fill_manual(values = c("#f1af8f", "#2398a0","#acc2c7"),name="Trial breakdown",breaks=c("1","2","3"),labels=c("no AEM", "pupil mismatch","pupil match"))+
  theme(legend.position = "bottom")+
  theme(panel.background = element_rect(fill = "#f5ebe1",colour = "#f5ebe1",size = 0.5, linetype = "solid"))+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank())+
  scale_y_continuous(labels = scales::percent,limits=c(0,1),breaks=seq(0,1,.2))
```

Average number of preswitch trials and post switch trials per baby, 
```{r}
#number of trials
coo <- ddply(orig.sample5,.(subID,block,switch),summarise,trials=length(unique(TRIAL_INDEX,na.rm = TRUE)))  

coo2 <- ddply(coo,.(subID,switch),summarise,trialavg=mean(trials,na.rm = TRUE),setrials=sd(trials, na.rm = TRUE)/sqrt(length(trials)))

coo3 <- ddply(coo2,.(switch),summarise,trialavg2=mean(trialavg,na.rm = TRUE),setrials=sd(trialavg, na.rm = TRUE)/sqrt(length(trialavg)))

dodge <- position_dodge(width=0.9)
limits <- aes(ymax = trialavg2 + setrials, ymin=trialavg2 - setrials)

ggplot(coo3,aes(x=factor(switch),y=trialavg2,color=factor(switch),fill=factor(switch)))+
  geom_bar(stat="identity",position=dodge)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Switch", y = "Number of trials")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  guides(color=FALSE)+
  scale_fill_brewer(palette="Set2")+
  scale_color_brewer(palette="Set2")+
  theme(legend.position = "none")+
  theme(legend.title=element_blank())+
  geom_errorbar(limits, width=0.25,position = position_dodge(0.9),color="black")+
  scale_y_continuous(limits=c(0,9),breaks=seq(0,9,1))+
  scale_x_discrete(breaks=c("1","2"),labels=c("Pre-switch", "Post-switch"))

#number of babies
doo <- ddply(orig.sample5,.(block,switch),summarise,numbabies=length(unique(subID,na.rm = TRUE)))  
doo2 <- ddply(doo,.(switch),summarise,babiesavg=mean(numbabies,na.rm = TRUE),sebabies=sd(numbabies, na.rm = TRUE)/sqrt(length(trials)))

dodge <- position_dodge(width=0.9)
limits <- aes(ymax = babiesavg + sebabies, ymin=babiesavg - sebabies)

ggplot(doo2,aes(x=factor(switch),y=babiesavg,color=factor(switch),fill=factor(switch)))+
  geom_bar(stat="identity",position=dodge)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Switch", y = "Number of babies")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  guides(color=FALSE)+
  scale_fill_brewer(palette="Set2")+
  scale_color_brewer(palette="Set2")+
  theme(legend.position = "none")+
  theme(legend.title=element_blank())+
  geom_errorbar(limits, width=0.25,position = position_dodge(0.9),color="black")+
  scale_y_continuous(limits=c(0,12),breaks=seq(0,12,2))+
  scale_x_discrete(breaks=c("1","2"),labels=c("Pre-switch", "Post-switch"))

```

% of trials for 
correct and incorrect AEMs 
facet_wrap by pre vs post
```{r}
# number of trials
koo <- group_by(orig.sample5, subID, switch, trialtype.aem) %>%
  summarise(
    numoftrials=length(unique(TRIAL_INDEX,na.rm = TRUE))
  )

# total number of trials completed
numtrials <- group_by(koo, subID) %>%
  summarise(
    totaltrials=sum(numoftrials,na.rm = TRUE)
    )
             
# only want correct and incorrect AEM
koo2 <- subset(koo, trialtype.aem < 3)

# combine 
koo3 <- merge(koo2, numtrials)

# calculate %
koo3$percent <- koo3$numoftrials/koo3$totaltrials

# calculate mean and SD
koofinal <- group_by(koo3, switch, trialtype.aem) %>%
  summarise(
    meanTRIALS=mean(percent,na.rm = TRUE),
    seTRIALS=sd(percent, na.rm = TRUE)/sqrt(length(percent))
  )

# prepare to plot
split <- c(`1` = "Preswitch",`2` = "Postswitch")
limits <- aes(ymax = meanTRIALS + seTRIALS, ymin=meanTRIALS - seTRIALS)
dodge <- position_dodge(width=0.9)

ggplot(koofinal,aes(x=factor(trialtype.aem),y=meanTRIALS,color=factor(trialtype.aem),fill=factor(trialtype.aem)))+
  geom_bar(stat="identity",position=dodge)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Trial type", y = "% of experiment")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  guides(color=FALSE, fill=FALSE)+
  scale_fill_manual(values = c("#bebad9", "#fffcb7"))+
  scale_color_manual(values = c("#bebad9", "#fffcb7"))+
  theme(legend.position = "bottom")+
  scale_x_discrete(name="AEM type",breaks=c("1","2"),labels=c("Correct", "Incorrect"))+
  scale_y_continuous(labels=percent,limits=c(0,.1),breaks=seq(0,.1,.02))+
  facet_wrap(~switch,labeller = as_labeller(split))+
  geom_errorbar(limits, width=0.25,color="black")+
  theme(strip.text = element_text(size=16))

```

% of babies
correct and incorrect AEMs 
AEMS trial-by-trial within each block (i.e., Are they learning the correct location during the pre-switch blocks and then updating predictions over the post-switch blocks?)
facet_wrap by pre vs post
```{r}
# number of babies
koo <- group_by(orig.sample5, NEWTRIALNUM,TRIAL_INDEX, sub.blocks, block, switch, trialtype.aem) %>%
  summarise(
    numofbabies=length(unique(subID,na.rm = TRUE))
  )

# total number of babies
totalbabies <- group_by(koo, TRIAL_INDEX) %>%
  summarise(
    totalbabies=sum(numofbabies,na.rm = TRUE)
    )

#combine
koo <- merge(koo, totalbabies)

# percent of babies
koo$percentbabies <- koo$numofbabies / koo$totalbabies

# only want correct and incorrect AEM
loofinal <- subset(koo, trialtype.aem < 3)

# prepare to plot
split <- c(`1` = "Block 1: Preswitch",`2` = "Block 1: Postswitch",`3` = "Block 2: Preswitch",`4` = "Block 2: Postswitch",`5` = "Block 3: Preswitch",`6` = "Block 3: Postswitch")

dodge <- position_dodge(width=0.9)

ggplot(loofinal,aes(x=NEWTRIALNUM,y=percentbabies,color=factor(trialtype.aem),fill=factor(trialtype.aem)))+
  geom_bar(stat="identity",position=dodge)+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(x = "Trial number", y = "% of babies")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  guides(color=FALSE)+
  scale_fill_manual(values = c("#bebad9", "#fffcb7"),name="AEM type",breaks=c("1","2"),labels=c("Correct", "Incorrect"))+
  scale_color_manual(values = c("#bebad9", "#fffcb7"))+
  theme(legend.position = "bottom")+
  scale_x_continuous(limits=c(1,9),breaks=seq(1,9,1))+
  scale_y_continuous(labels=percent,limits=c(0,.6),breaks=seq(0,.6,.1))+
  facet_wrap(~sub.blocks,labeller = as_labeller(split),ncol = 2)+
  theme(strip.text = element_text(size=16))

```

where are babies looking? wrong side, right side, center
```{r}
lookscode <- subset(pupilbreakdown, lookattarget < 9) #only care about 100ms timebins that has good data

#type 1 = correct AEM to target, 2 = incorrect AEM to distractor, 3 = no AEM
#Calculate proplooking for each type of gaze (target, center, distractor)
lookscode$center <- 0
lookscode$distractor <- 0
lookscode$target <- 0  

lookscode$target[lookscode$lookattarget == 1] <- 1 #if lookattarget == 1, then looking at target
lookscode$center[lookscode$lookattarget == 5] <- 1 #if lookattarget == 5, then looking at center
lookscode$distractor[lookscode$lookattarget == 0] <- 1 #if lookattarget == 0, then looking at distractor

e2 <- ddply(lookscode,.(subID,timecode),summarise,TargProp=mean(target,na.rm = TRUE),CentProp=mean(center,na.rm = TRUE),DistProp=mean(distractor,na.rm = TRUE))

#collapse across subjects
e31 <- ddply(e2,.(timecode),summarise,
             looking=mean(TargProp,na.rm = TRUE),
             selooking=sd(TargProp, na.rm = TRUE)/sqrt(length(TargProp)))
e31$group <- 1
e32 <- ddply(e2,.(timecode),summarise,
             looking=mean(CentProp,na.rm = TRUE),
             selooking=sd(CentProp, na.rm = TRUE)/sqrt(length(CentProp)))
e32$group <- 2
e33 <- ddply(e2,.(timecode),summarise,
             looking=mean(DistProp,na.rm = TRUE),
             selooking=sd(DistProp, na.rm = TRUE)/sqrt(length(DistProp)))
e33$group <- 3

efinal <- rbind(e31,e32,e33)

#group 1 - target, 2 = center, 3 = distractor
vlines <- c(250,1750,2550)
ggplot(efinal,aes(x=timecode,y=looking,color=factor(group),fill=factor(group)))+
  geom_line()+theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("Where are babies looking?")+
  labs(x = "Time", y = "% of looking")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=16),axis.text.y  = element_text(size=16))+
  theme(legend.text=element_text(size=20),legend.title=element_text(size=20))+
  geom_ribbon(aes(ymin=looking-selooking,ymax=looking+selooking),alpha=0.4)+
  geom_vline(xintercept = vlines)+
  scale_x_continuous(limits=c(0,4000),breaks=seq(0,4000,500), expand = c(0, 0))+
  scale_y_continuous(labels = scales::percent,limits=c(0,1),breaks=seq(0,1,0.2))+
  guides(color=FALSE)+
  scale_fill_brewer(palette="Set1",name="Where are babies looking",breaks=c("1","2","3"),labels=c("Correct side", "Center","Wrong side"))+
  scale_color_brewer(palette="Set1")+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(legend.position = "top")

#by switch
e2 <- ddply(lookscode,.(subID,switch,timecode),summarise,TargProp=mean(target,na.rm = TRUE),CentProp=mean(center,na.rm = TRUE),DistProp=mean(distractor,na.rm = TRUE))

#collapse across subjects
e31 <- ddply(e2,.(switch,timecode),summarise,
            looking=mean(TargProp,na.rm = TRUE),
            selooking=sd(TargProp, na.rm = TRUE)/sqrt(length(TargProp)))
e31$group <- 1
e32 <- ddply(e2,.(switch,timecode),summarise,
            looking=mean(CentProp,na.rm = TRUE),
            selooking=sd(CentProp, na.rm = TRUE)/sqrt(length(CentProp)))
e32$group <- 2
e33 <- ddply(e2,.(switch,timecode),summarise,
            looking=mean(DistProp,na.rm = TRUE),
            selooking=sd(DistProp, na.rm = TRUE)/sqrt(length(DistProp)))
e33$group <- 3

efinal <- rbind(e31,e32,e33)
#group 1 - target, 2 = center, 3 = distractor

split <- c(`1` = "Correct side",`2` = "Center",`3` = "Wrong side")
ggplot(efinal,aes(x=timecode,y=looking,color=factor(switch),fill=factor(switch)))+
  geom_line()+theme_bw()+theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("Where are babies looking?")+
  labs(x = "Time", y = "% of looking")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=14),axis.text.y  = element_text(size=14))+
  theme(legend.text=element_text(size=14),legend.title=element_text(size=14))+
  geom_ribbon(aes(ymin=looking-selooking,ymax=looking+selooking),alpha=0.4)+
  geom_vline(xintercept = vlines)+
  scale_x_continuous(limits=c(0,4000),breaks=seq(0,4000,500), expand = c(0, 0))+
  scale_y_continuous(labels = scales::percent,limits=c(0,1),breaks=seq(0,1,0.2))+
  guides(color=FALSE)+
  facet_wrap(~group,labeller = as_labeller(split),dir="v")+
  theme(strip.text = element_text(size=14))+
  scale_fill_brewer(palette="Set2",name="Sub-block",breaks=c("1","2"),labels=c("Pre-switch", "Post-switch"))+
  scale_color_brewer(palette="Set2")+
  theme(legend.position = "top")+
  theme(plot.title = element_text(hjust = 0.5))

```

main pupil timecourse plot for pre and post
```{r}
boo1 <- ddply(orig.sample5,.(subID,switch,TIMECODE),summarise,pupil=mean(PUPIL_CORRECTED,na.rm = TRUE)) #collapse across trials
boo1 <- subset(boo1, TIMECODE < 4001)
boo2 <- ddply(boo1,.(switch,TIMECODE),summarise,pupilavg=mean(pupil,na.rm = TRUE),sepupil=sd(pupil, na.rm = TRUE)/sqrt(length(pupil))) #collapse across subs
vlines <- c(250,1750,2550)

ggplot(boo2,aes(x=TIMECODE,y=pupilavg,color=factor(switch),fill=factor(switch)))+
  geom_line()+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("Timecourse: Pupil Change")+
  labs(x = "Time", y = "Pupil change from baseline (%)")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_ribbon(aes(ymin=pupilavg-sepupil,ymax=pupilavg+sepupil),alpha=0.4)+
  geom_vline(xintercept = vlines)+
  scale_x_continuous(limits=c(0,4000),breaks=seq(0,4000,500), expand = c(0, 0))+
  scale_fill_brewer(palette="Set2",breaks=c("1","2"),labels=c("Pre-switch", "Post-switch"))+
  scale_color_brewer(palette="Set2")+guides(color=FALSE)+
  scale_y_continuous(labels = scales::percent,limits=c(-0.1,.1),breaks=seq(-0.1,.1,.02), expand = c(0, 0))+theme(legend.title=element_blank())+theme(legend.position = "top")+
  theme(plot.title = element_text(hjust = 0.5))
  
```

Pupil change from baseline for each subject
```{r}
noo <- group_by(orig.sample5, subID, TRIAL_INDEX) %>%
  summarise(
    pupilsize = mean(PUPIL_CORRECTED, na.rm = TRUE)
  )

noo2 <- group_by(noo, subID) %>%
  summarise(
    pupilavg=mean(pupilsize,na.rm = TRUE),
    sepupil=sd(pupilsize, na.rm = TRUE)/sqrt(length(pupilsize))
  )

limits <- aes(ymax = pupilavg + sepupil, ymin=pupilavg - sepupil)

ggplot(noo2,aes(x=factor(subID),y=pupilavg,color=factor(subID),fill=factor(subID)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_bar(stat = "identity")+
  labs(x = "Sub ID", y = "Pupil change from baseline")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  scale_y_continuous(labels=percent,limits=c(-.05,.05),breaks=seq(-.05,.05,0.01))+
  geom_errorbar(limits, width=0.25,color="black")

# DISTRIBUTION

ggplot(noo,aes(x=factor(subID),y=pupilsize,color=factor(subID),fill=factor(subID)))+
  theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(),axis.line = element_line(colour = "black"))+
  geom_point()+
  labs(x = "Sub ID", y = "Pupil change from baseline")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  theme(legend.position="none")+
  scale_y_continuous(labels=percent,limits=c(-.15,.2),breaks=seq(-.15,.2,0.05))
```

eccentricity timecourse plot 
```{r}
# screen res is 1024 x 1280 (Y X)
#a. Y coordinate timecourse, pre and post
#line graph
boo <- subset(orig.sample5, TIMECODE < 4001)
boo$RIGHT_GAZE_X2 <- abs(boo$RIGHT_GAZE_X-640)

boo1 <- ddply(boo,.(subID,switch,TIMECODE),summarise,xcoordinate=mean(RIGHT_GAZE_X2,na.rm = TRUE)) #collapse across trials
boo2 <- ddply(boo1,.(switch,TIMECODE),summarise,Xavg=mean(xcoordinate,na.rm = TRUE),seX=sd(xcoordinate, na.rm = TRUE)/sqrt(length(xcoordinate))) #collapse across subs
vlines <- c(250,1750,2550)

ggplot(boo2,aes(x=TIMECODE,y=Xavg,color=factor(switch),fill=factor(switch)))+
  geom_line()+theme_bw()+
  theme(panel.grid.major = element_blank(),panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  ggtitle("Timecourse: eccentricity")+
  labs(x = "Time", y = "absolute distance from center of screen")+
  theme(plot.title = element_text(face="bold", size=20, hjust=0))+
  theme(axis.title = element_text(face="bold", size=20))+ 
  theme(axis.text.x  = element_text(size=20),axis.text.y  = element_text(size=20))+
  theme(legend.text=element_text(size=16),legend.title=element_text(size=16))+
  geom_ribbon(aes(ymin=Xavg-seX,ymax=Xavg+seX),alpha=0.4)+
  geom_vline(xintercept = vlines)+
  scale_x_continuous(limits=c(0,4000),breaks=seq(0,4000,500), expand = c(0, 0))+
  guides(color=FALSE)+
  scale_y_continuous(limits=c(0,400),breaks=seq(0,400,50), expand = c(0, 0))+
  scale_fill_brewer(palette="Set2",breaks=c("1","2"),labels=c("Pre-switch", "Post-switch"))+
  scale_color_brewer(palette="Set2")+guides(color=FALSE)+
  theme(legend.title=element_blank())+
  theme(legend.position = "top")+
  theme(plot.title = element_text(hjust = 0.5))
```
